A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-15 paper.tex
fix typo

Secure Pub-Sub model\cite{SPS}, a brokerless desig, is proposed to eliminate the security risk of middleware and to provide a reputation-based fairness payment strategy on blockchain.
The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent. Yet, without brokers, participants may need to reveal more sensitive information in order to communicate. By Paolo Missier et. al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace which enables trading with Ethereum smart contracts. The brokers are only responsible for data transmission in order to adapt flexible agreement between participants. However, the data cubes (i.e., a tuple of data information) are stored in a centralized Cassandra database, guaranteed to be tamper-proof but the risk of single point failure still exists.

>>>>

Secure Pub-Sub model\cite{SPS}, a brokerless design, is proposed to eliminate the security risk of middleware and to provide a reputation-based fairness payment strategy on blockchain.
The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent. Yet, without brokers, participants may need to reveal more sensitive information in order to communicate. By Paolo Missier et. al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace which enables trading with Ethereum smart contracts. The brokers are only responsible for data transmission in order to adapt flexible agreement between participants. However, the data cubes (i.e., a tuple of data information) are stored in a centralized Cassandra database, guaranteed to be tamper-proof but the risk of single point failure still exists.
